---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/paulnorthrop/stat0002?branch=master&svg=true)](https://ci.appveyor.com/project/paulnorthrop/stat0002)
[![R-CMD-check](https://github.com/paulnorthrop/accessr/workflows/R-CMD-check/badge.svg)](https://github.com/paulnorthrop/accessr/actions)

## accessr

This package provides functions to produce accessible html slides, html, Word and PDF documents from input R markdown files.  A main aim is to enable documents of different formats to be produced from a **single** R markdown source file using a single function call.  The `render()` function from the [rmarkdown package](https://cran.r-project.org/package=rmarkdown) is used to render R markdown files. A zip file containing multiple files can be produced from afingle function call.  A user-supplied template Word document can be used to determine the formatting of the output Word document. When the output format is a Word document the `knitr` chunk options `out.width` and/or `out.height` can be used to set the dimensions of a figure (R-generated or external image).  This functionality is not normally available. Accessible PDF files are produced from Word documents using [OfficeToPDF](https://github.com/cognidox/OfficeToPDF).  A convenience function, `install_otp()` is provided to install this software. The option to print html output to (non-accessible) PDF files is also available.  

### Installation

```{r installation, eval = FALSE}
# Install package remotes, if necessary
install.packages("remotes")
remotes::install_github("paulnorthrop/accessr")
```

If you are using RStudio then it may be a good idea to close RStudio and re-open it.

### Getting started

```{r, eval = FALSE}
library(accessr)
?accessr
```

The main functions are:

* `install_otp`: convenience function to install OfficeToPDF (required to produce an accessible PDF file from a Word document).
* `rmd2word()`: create word documents and accessible PDF files.
* `rmd2ioslides(), rmd2slidy`: create isoslides/slidy presentations and perhaps print to (non-accessible) PDF documents.
* `rmd2html()`: create html documents and perhaps print to (non-accessible) PDF documents.

Each function provides the option to create a zip archive containing the output files.  All the .Rmd files in a directory can be processed with one function call.
Information such as `title`, `author`, `lang` etc in the YAML header in the Rmd file are used but `output` is ignored.

### Rmd to Word to PDF

Suppose that in your current working directory you have the R markdown files `file1.Rmd` and `file2.Rmd`, a template Word file `your_template.docx` and that the file `OfficeToPDF.exe` downloaded from [OfficeToPDF releases](https://github.com/cognidox/OfficeToPDF/releases) is either in your working directory or in a directory listed in `searchpaths()`.  Then the following will create files `file1.docx`, `file2.docx`, `file1.pdf` and `file2.pdf` in your working directory and, unless you supply `zip = FALSE`, a zip file `accessr_word.zip` containing the two PDF files will also be created.

```{r, eval = FALSE}
rmd2word(c("file1", "file2"), doc = "your_template.docx")
```

A path to the Word template document can be provided using the `doc` argument.  If `doc` is not provided then a default template is used. See `?rmd2word` for details. If you include figures then the `knitr` chunk option `fig.alt` can be used to set the alternative text. You may find you need to enclose LaTeX maths environments in \$\$ ... \$\$ when typesetting mathematics. 

A path to the `OfficeToPDF.exe` file can be provided using an argument `dir`. If `dir` is missing then `rmd2word` will look for OfficeToPDF.exe in the default installation directory `dir` of `install_otp`. 

### Rmd to ioslides 

Similarly, the function `rmd2ioslides` produces HTML [ioslides](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html) presentations.

```{r, eval = FALSE}
rmd2ioslides(c("file1", "file2"))
```

If the argument `pdf = TRUE` is supplied then the `chrome_print` function in the `pagedown` package is used to produce (non-accessible) PDF files from these slides.  This requires a secure internet connection. See `?rmd2ioslides`.

`rmd2slidy` (see [slidy](https://bookdown.org/yihui/rmarkdown/slidy-presentation.html) presentations) and `rmd2html` work in a similar way.

### A basic example Rmd file

Executing the following code will copy the file `example.Rmd` to the working directory an create from it output as a Word document, an html document and ioslides and slidy presentations. The default is to produce a zip file from each of these four function calls. In the working directory there will also be the files `example.docx`, `example.pdf` and `example.html`. The latter contains the slidy presentation because the final three calls each create `example.html`, which is overwritten.

```{r exampleRmd, eval = FALSE}
rmd_file <- system.file(package = "accessr", "examples", "example.Rmd")
file.copy(from = rmd_file, to = getwd())
rmd2word("example")
rmd2html("example")
rmd2ioslides("example")
rmd2slidy("example")
```

This example file includes examples of creating figures and tables and describes potential issues with typesetting mathematics when creating Word output.

### Suggested workflow

I found that using `rmd2ioslides` to create presentations and then `rmd2word` to create (zip files containing) accessible PDF versions of these presentations enabled me quickly to upload files to a VLE like Moodle.

