---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/paulnorthrop/stat0002?branch=master&svg=true)](https://ci.appveyor.com/project/paulnorthrop/stat0002)

## accessr

Accessible PDF documents are produced by creating Word documents from R markdown files and then PDF documents from these Word documents.  The first step uses the `render` function from the [rmarkdown package](https://cran.r-project.org/package=rmarkdown).  The second step uses [OfficetoPDF](https://github.com/cognidox/OfficeToPDF).

### Installation

```{r installation1, eval = FALSE}
install.packages("remotes")
```

You only need to do this once.  

```{r installation2, eval = FALSE}
remotes::install_github("paulnorthrop/accessr")
```

If you are using RStudio then it may be a good idea to close RStudio and re-open it.

### Getting started

```{r, eval = FALSE}
library(accessr)
?accessr
```

### An example

Suppose that in your current working directory you have the R markdown files `file1.Rmd` and `file2.Rmd`, a template Word file `template.docx` and that the file `officetopdf.exe` downloaded from [OfficeToPDF releases](https://github.com/cognidox/OfficeToPDF/releases) is either in your working directory or in a directory listed in `searchpaths()`.  Then the following will create files `file1.docx`, `file2.docx`, `file1.pdf` and `file2.pdf` in your working directory.

```{r, eval = FALSE}
rmd2pdf(c("file1", "file2"), doc = "template.docx")
```

A path to the Word template document can be provided using the `doc` argument.  If `doc` is not provided then a default template is used.  A path to the `officetopdf.exe` file can be provided using an argument `dir`. 
