---
title: "An overview of accessr"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{An overview of accessr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: accessr.bib
csl: taylor-and-francis-chicago-author-date.csl
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(accessr)
```

Create an example Rmd document.  
Put it somewhere.
How best to illustrate it?
what does officedown/officer do?
See https://ardata-fr.github.io/officeverse/officedown-for-word.html

Could produce the vignette as 

Word
PDF from Word
isoslides, slidy and html (plus printed as PDF)


## Mathematics

\mbox{} not {\rm }

equation numbering?

Dollar signs needed for maths environment

## R markdown document

### 

### Figures

knitr::include.graphics()

fig.alt

out.width and out.height

### Tables

huxtable, kable?, base R markdown? flextable?

## Word

templates

## Ioslides presentation

## Slidy presentation

## HTML document




@officedown

@officer


